\LARGE \bf Energy-Aware Dynamic Planning Algorithm for Autonomous UAVs

### 2020-12-09 icra-2021.tex
changes ... (2)

\leavevmode\thispagestyle{empty}\newpage % just for now

\bibliographystyle{IEEEtran}
\bibliography{\jobname}

@@

\section{Plan Specification Format}
\label{app:plan-spec}

@@

This means that for the first stage, the algorithm can alter the trajectory satisfying $\varphi_1\in\mathbb{C}_1$, and it can alter the computations individually. In fact the $j$-th computation parameter has to be in $\mathbb{S}_{1,j}$.

Follows the entries for stage $\Gamma_2$, $\Gamma_3$ and so on, until the last stage. We assume that the last triggering point is the final UAV position.

\section{Plan Specification Example}
\label{app:plan-example}
We discuss how to specify an initial mission plan with an example of a survey mission. The reader can later execute the initial mission plan using the simulator in Appendix~\ref{app:simulator}. The plan is user-defined. It specifies the trajectory and tasks of a mission along the QoS and TEEs sets.

@@

\section{Components Specification Format}

>>>>

\leavevmode\thispagestyle{empty}\newpage
\leavevmode\thispagestyle{empty}\newpage % just for now

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliographystyle{IEEEtran}
\bibliography{\jobname}

@@

\section{Plan Specification}

\subsection{Format}
\label{app:plan-spec}

@@

This means that for the first stage, the algorithm can alter the trajectory satisfying $\varphi_1\in\mathbb{C}_1$. It can alter the computations individually. In fact the $j$-th computation parameter has to be in $\mathbb{S}_{1,j}$.

Follows the entries for stage $\Gamma_2$ (equivalent to lines~\ref{code:stage}--\ref{code:parameter-set}), $\Gamma_3$ and so on, until the last stage. We assume that the last triggering point is the final UAV position.

\subsection{Example}
\label{app:plan-example}

We discuss how to specify an initial mission plan with an example of a survey mission. The reader can later execute the initial mission plan using the simulator in Appendix~\ref{app:simulator}. The plan is user-defined. It specifies the trajectory and tasks of a mission along the QoS and TEEs sets.

@@
